---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PDXpower

<!-- badges: start -->
[![metacran downloads](https://cranlogs.r-pkg.org/badges/PDXpower)](https://cran.r-project.org/package=PDXpower)
[![](https://cranlogs.r-pkg.org/badges/grand-total/PDXpower)](https://cran.r-project.org/package=PDXpower)
[![CRAN_time_from_release](https://www.r-pkg.org/badges/ago/PDXpower)](https://cran.r-project.org/package=PDXpower)
[![CRAN_Status_Badge_version_last_release](https://www.r-pkg.org/badges/version-last-release/PDXpower)](https://cran.r-project.org/package=PDXpower)
<!-- badges: end -->

The `PDXpower` package can conduct power analysis for time-to-event outcome based on empirical simulations.

## Installation

You can install the development version of `PDXpower` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("shanpengli/PDXpower")
```

## Example

Below is a toy example how to conduct power analysis based on a preliminary dataset `mice1`. Particularly, we need to specify a formula that fits a ANOVA mixed effects model with correlating variables in `mice1`, where `ID` is the PDX line number, `Y` is the event time variable, and `Tx` is the treatment variable.

Next, run power analysis by fitting a ANOVA mixed effects model on `mice1`.
```{r}
library(PDXpower)
data(mice1)
### Power analysis on a preliminary dataset by assuming the time to event is log-normal
PowTab <- PowANOVADat(data = mice1, formula = log(Y) ~ Tx, 
                      random = ~ 1|ID, n = c(3, 5, 10), m = c(2, 3, 4), sim = 100)
PowTab
```

The following code generates a power curve based on the object `PowTab`.
```{r}
plotpower(PowTab[[4]], ylim = c(0, 1))
```

Or we can fit a ANOVA fixed effect model for running power analysis.
```{r}
PowTabfit <- PowANOVADat(data = mice1, formula = log(Y) ~ Tx, 
                      random = ~ 1|ID, n = c(3, 5, 10), m = c(2, 3, 4), fixed.effect = TRUE, sim = 100)
PowTabfit
```

Alternatively, one can run power analysis by fitting a Cox frailty model. Here we present another dataset `mice2`. Particularly, we need to specify a formula that fits a Cox frailty model with correlating variables in `mice2`, where `ID` is the PDX line number, `Y` is the event time variable, `Tx` is the treatment variable, and `status` is the event status.
```{r, eval=TRUE}
data(mice2)
### Power analysis on a preliminary dataset by assuming the time to event is Weibull-distributed
PowTab <- PowFrailtyDat(data = mice2, formula = Surv(Y, status) ~ Tx + cluster(ID), 
                        n = c(3, 5, 10), m = c(2, 3, 4), sim = 100)
PowTab
```

The following code generates a power curve based on the object `PowTab`.
```{r}
plotpower(PowTab[[5]], ylim = c(0, 1))
```

Or we can fit a Cox fixed effect model for running power analysis.
```{r}
PowTabfit <- PowFrailtyDat(data = mice2, formula = Surv(Y, status) ~ Tx + cluster(ID), 
                           n = c(3, 5, 10), m = c(2, 3, 4), fixed.effect = TRUE, sim = 100)
PowTabfit
```

Alternatively, we may also conduct power analysis based on median survival of two randomized arms. We suppose that the median survival of the control and treatment arm is 2.4 and 4.8, allowing a PDX line has 10% marginal error (`tau2=0.1`) of treatment effect and an exponential event time, a power analysis may be done as below:
```{r, eval=TRUE}
### Assume the time to event outcome is weibull-distributed
PowTab <- PowFrailty(ctl.med.surv = 2.4, tx.med.surv = 4.8, nu = 1, tau2 = 0.1, sim = 100,
                     n = c(3, 5, 10), m = c(2, 3, 4))
PowTab
```


```{r}
### Assume the time to event outcome is log-normal
PowTab <- PowANOVA(ctl.med.surv = 2.4, tx.med.surv = 4.8, tau2 = 0.1, sigma2 = 1, sim = 100,
                   n = c(3, 5, 10), m = c(2, 3, 4))
PowTab
```



