---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PDXpower

<!-- badges: start -->
<!-- badges: end -->

The `PDXpower` package can conduct power analysis for time-to-event outcome based on empirical simulations.

## Installation

You can install the development version of `PDXpower` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("shanpengli/PDXpower")
```

## Example

Below is a toy example how to conduct power analysis based on a preliminary dataset using the `PowFrailtyDat` function. Particularly, we need to specify a formula that fits a Cox Frailty model with correlating variables in `data`, where `Y` is the event time variable, `status` is the event indicator, `Tx` is the treatment variable, and `ID` is the PDX line variable.

```{r, eval=TRUE}
library(PDXpower)
## simulate a dataset with a Weibull event outcome as a preliminary dataset
data <- SimPDXdata(seed = 1000, n = 3, m = 3, beta = -0.8, tau2 = 0.2, lambda = 0.03,
nu = 2, sigma2 = 1, distr = "Weibull", lambdaC = 0.1, censor = TRUE)

PowTab <- PowFrailtyDat(data = data, formula = Surv(Y,status) ~ Tx + cluster(ID),
n = c(3, 5, 10), m = c(2, 3, 4), sim = 100)
PowTab
plotpower(PowTab, ylim = c(0, 1))
```

Alternatively, we may also conduct power analysis based on median survival of two randomized arms using the `PowFrailty` function. We suppose that the median survival of the control and treatment arm is 2.4 and 4.8, allowing a PDX line has 10% marginal error (`tau2=0.1`) of treatment effect and an exponential event time, a power analysis may be done as below
```{r, eval=TRUE}
library(PDXpower)
PowTab <- PowFrailty(ctl.med.surv = 2.4, tx.med.surv = 4.8, sim = 100, nu = 1, tau2 = 0.1,
n = c(3, 5, 10), m = c(2, 3, 4))
PowTab
plotpower(PowTab, ylim = c(0, 1))
```
